Embedded Scalars, Preferred Readings \& Prosody: {A}n Experimental Revisit

### 2015-02-21 text/paper/revision_01/paper.tex
Petra edits
final edits K2 revision 01 MF

To deal with these methodological problems, this paper presents
results from an experimental study which presented sentence materials
auditorily and explicitly manipulated contrastive stress on embedded
scalar items. We employed an \mymark{incremental verification task} in
which parts of a to-be-evaluated picture were hidden and only revealed
piece-wise at the participants’ request until they felt able to give a
binary truth-value judgement \citep[see][]{Conroy2008}. We use both a
classical regression analysis and a Bayesian statistical model to
analyze the data from this novel task, and validate this method by
including control conditions testing ambiguous sentences with a
well-known preference on available readings. We argue that this method
provides categorical behavioral data that is both clearly indicative
of the reading preferences among participants and largely independent
of potential pictorial confounds, such as the mentioned typicality
effects.

@@

The paper is structured as follows. Section~\ref{sec:get-know-your}
elaborates on the three kinds of relevant readings for our target
sentences. Section~\ref{sec:theories-predictions} works out plausible
\emph{ex ante} predictions of \emph{traditionalism} and
\emph{grammaticalism}. Section~\ref{sec:previous-studies} reviews
related experimental studies to the extent necessary to motivate our
own approach. Section~\ref{sec:exp} describes our experimental design,
analyses and results. Finally, Section~\ref{sec:critical-reflection}
discusses our method and interpretation of the results in a broader
theoretical context.

@@

\paragraph{General Idea.} In order to test the availability and
preferences of different readings of \as- and \es-sentences in German,
we were looking for a way to unambiguously map responses from a
picture verification task to specific readings. We were particularly
interested in the question whether local readings would be observed at
all, and whether their presence or absence would be modulated by a
contrastive accent on the scalar item. Moreover, we were interested in
obtaining information about the relative preferences of the different
readings. In addition, we wanted to minimize potential picture
typicality effects. To achieve this (see
Section~\ref{sec:discussion-1} for discussion), we used an
\mymark{incremental verification task} (\acro{ivt}), which is a
modified version of picture verification
\citep[see][]{Conroy2008}. The general idea is that subjects are
requested to judge sentence material with respect to pictures that do
not necessarily contain all the information relevant for judging a
certain reading true or false. In that case, participants can demand
that more information be revealed. Participants are instructed to make
a truth-value judgment as soon as they are able to. When they do, the
trial ends.

@@

The number of responses that fell out of our classification scheme
differs substantially between \as- and \es-conditions. There are 7.0\%
/ 4.4\% unclassifiable judgements in the neutral / accented
\as-conditions, but 19.3\% / 17.6\% in the neutral / accented
\es-conditions respectively. A look at the left-hand side of
Table~\ref{tab:count_data_CC} reveals that there is some systematicity
in 'error' answers. Most answers that we classified as 'errors' have a
plausible explanation: random errors, a handful of mistakes resulting
from confusing buttons for \emph{true} and \emph{false} and a few
'spill-over errors' where participants gave responses one position too
late. There is one notable exception, though. A substantial number of
\emph{true} responses were given at the second position of
\es-sequences (9.7\% / 8.8\%) which is shown in
Figure~\ref{fig:exseqES2}. Although this position in the sequence is
the critical position to reveal a global reading, the latter would be
indicated by a \emph{false} response. Given the low number of possible
mistakes resulting from confusion buttons for \emph{true} and
\emph{false} elsewhere, this seems to be a more systematic pattern. It
appears as if subjects read \es-sentences as if the non-monotonic
quantifier \emph{exactly one} was a monotonic \emph{at least one},
without pragmatic enrichment of \emph{some}. 16 out of the total 21
answers in this category come from 5 subjects, while the remaining 5
were single answers by 5 different subjects.
% subjects 1, 9, 12, 21, 84
This suggests that at least for some subjects non-monotonic
quantifiers were problematic. (We will come back to this intriguing
observation later in Section~\ref{sec:discussion-1}, where we suggest
that a non-monotonic reading of \emph{exactly one} might also explain
the high number of \emph{true} answers in step 5 of the
\es-conditions.)

@@

\paragraph{Summary \& Interpretation.} The present study investigated
prosodic effects on quantifier interpretation by employing a new
experimental paradigm, the incremental verification task. We were
specifically interested in whether ``local readings'' of sentences
where \emph{some} is embedded under another quantifier can be found,
and how salient these readings are under varying prosody of auditorily
presented sentence material, in particular the presence or absence of
contrastive stress on embedded \emph{some}.

High scores of success in control conditions show that participants
understood the incremental verification task and were able to give
judgements at the right point in a picture sequence. Results for the
preference-related controls show that our design is able to detect
multiple readings and preferences among these. Crucially, the amount
of response types for \lc- and \ec-readings reflected the known
preference for the former, with a mild bias for readings that can be
judged later in the sequence. Also, the incremental verification task
was generally sensitive to prosody. However, our regression analysis
showed that significant prosodic effects were restricted to
preference-related controls. Contrastively, the Bayesian analysis
showed that accenting scalar \emph{some} generally led to more local
readings, but that effect was not significant. Local readings occurred
in \es-sentences, independently of prosody, but required prosodic
marking in \as-sentences. Our analyses support the impression that
inspection of the raw data gives, namely that the general qualitative
pattern of reading preferences is the same for \as- and
\es-conditions: literal readings are preferred over local readings
which are preferred over global readings. More concretely, our
analyses suggest the following preference patterns (bracketed readings
are not supported by our data and the previous analyses):

@@

Traditionalism easily explains the absence of global readings. Weak
traditionalism, introduced in Section~\ref{sec:traditionalism}, for
instance, would hold that the extra assumptions needed to derive
global readings (e.g., a speaker competence assumption) are not
available or only allow for epistemically weak implicatures that would
show as responses indicative of literal readings in our task. In
support of this view, traditionalists could argue that the task's
rather high processing demands lead to a suppression of global
readings, in line with the findings of
\citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
load negatively affects the number of scalar implicature responses in
sentence verification tasks. The finding of local readings in
\as-sentences with contrastive stress is easily explained by adopting
the prosodic markedness hypothesis. What traditionalism does not
predict is the high number of answers indicative of local readings in
the \es-conditions. Resorting to the prosodic markedness hypothesis
does not help, because local readings were observed for accented as
well as for unaccented \es-sentences. It would also remain unclear why
prosodic cues should have such differential effects on \as- and
\es-sentences.

@@

On conceptual grounds we are very much in favor of a disambiguation
criterion in terms of economy considerations, but whether the
particular account sketched here is empirically successful in other
cases as well, must remain to be seen. Two things are worth
emphasizing here nonetheless. Firstly, the sketched Magri-style
account is a plausible alternative \emph{post hoc} explanation. It was
not, at least to our knowledge, a salient possibility before seeing
our data set: other specifications of $Alt_1$ and $Alt_2$ could have
been made equally plausible \emph{ex ante}. Secondly, what our data
refutes is that preferences for readings follow logical
strength. This, therefore, does not jeopardize grammaticalism as a
core theory, but calls for theory-internal revision of its
disambiguation criterion. Taken together, we argue that the data
presented here points to a dire need of refining grammaticalism,
perhaps along the lines suggested here, but ideally alongside more
empirical data like the one we presented.

\paragraph{Traditionalism.} Traditionalism, as we described it in
Section~\ref{sec:theories-predictions}, can also not account for the
observed pattern of results. It has to explain the possibility of
local readings of prosodically unmarked \es-sentences, and, perhaps,
also the large number of local readings in accented \es-sentences
compared to the much lower number in accented \as-sentences. To do so
within a strict traditionalist framework seems difficult. A first
option might be to account for alleged local readings as the result of
some other phenomenon, such as typicality or contrast
\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter}.
Since this ties into a critical reflection on our design, we will
enlarge on the possibility of typicality- and contrast-based effects
in our setting. Eventually, we argue that contrast-effects alone are
unlikely to explain the observed high number of local answers in
\es-sentences, but that a ``modern traditionalist'' explanation of the
answer pattern might be available if we allow for the possibility that
\emph{exactly one} gets an unexpected ``referential interpretation.''

@@

The foregoing interpretation and discussion presupposed that the
interpretation of our data, given in Section~\ref{sec:discussion-1},
was sound. But there are a number of conceivable objections to our
design and our interpretation of the presented results, which
essentially cast into doubt that our data suggests the preference
relation in (\ref{bsp:observed-preferences}). We will consider the
most pressing ones in the following.

@@

\paragraph{Incomparability of target conditions and preference-related
  controls.} One could object that it is not feasible to compare
results from the preference-related controls to results from our
target conditions, because the source of different readings is
fundamentally different. In the former we have a syntactic ambiguity,
in the latter a set of putative pragmatic enrichments. The former is a
case of perceived ambiguity (some of our subjects reported this), the
latter arguably is not
\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
if the distribution of responses is indicative of the known preference
patterns in preference-related controls, this would not necessarily
mean that the distribution of responses in target conditions is
indicative of preference relations in the same way.

@@

To address this worry we ran another stripped-down version of the
\ivt. We recruited 50 subjects via Amazon's Mechanical Turk and paid
them 1 US\$ compensation. Similar to our main experiment, the
post-experiment started with two training trials with unambiguous
sentences, familiarizing our subjects with the task. In the
browser-based version, alert boxes pointed out subjects' mistakes when
they tried to exit to early, chose the wrong response or tried to
unravel the sequence further than strictly necessary. The main part of
the experiment consisted of six trials, two of which were critical and
four of which were controls. On critical trials, each subject saw
different version of sentences like (\ref{bsp:Item-PostExp}), in
connection with sequences like in Figure~\ref{fig:Trial-PostExp}.

@@

If we accept that the \ivt is sensitive to implicature-based
ambiguities, what is left to worry about is that information about
response biases (early vs.~late) do not carry over from the
preference-related control conditions to the target conditions in the
main experiment. It could be, after all, that the task triggers
subjects to exit late for perceived syntactic ambiguities and to exit
early for ``pragmatic ambiguities'' involving implicature
readings. This might also possibly explain why there are more `error'
responses on the last position in the preference-related controls. But
none of this has any serious impact on the suggested preference
relation in (\ref{bsp:observed-preferences}). For even if, as possibly
the post-experiment suggests as well, there is a sequential bias in
the target conditions to exit early, the main effect of such a bias
would merely be that we should consider local readings more salient
than we do now. In the light of the data from main and
post-experiments, it would be far-fetched to uphold that our data
indicates that local readings are at least as salient as literal
ones. But that means that the suggested interpretation in
(\ref{bsp:observed-preferences}) still holds, and all the problems
that we identified for (the considered versions of) traditionalism and
grammaticalism apply.

To strengthen this case further, let us assume that the \ivt is
entirely incapable of reliably indicating preferences among candidate
pragmatic enrichments of the relevant kind. Can we still draw any
conclusions about mere availability (non-negligible salience) of
readings? At a minimum, we would like to uphold that local readings
are available in \es-sentences and that global readings are unattested
in \as- and \es-sentences. But that alone is not predicted by either
traditionalism or grammaticalism in the guises that we considered. The
former cannot explain the substantial number of local responses in
\es-sentences, the latter does not explain the total absence of global
responses.\todo{skip this paragraph?}

@@

Still, we readily admit that our model is highly simplistic. Several
aspects are especially noteworthy here. Firstly, we did not
distinguish different types of errors, and did not take into account
that when errors occurred earlier in the sequence, later decision
points could no longer be reached. This way the model may actually
have unduly de-emphasized the salience of readings that can be judged
later in a sequence. Another, more complicated model of the likelihood
of answer patterns, might therefore have given support to
quantitatively different conclusions. Unfortunately, it is not clear
how exactly such a more complex generating model should be
set-up. Eventually, a full processing model, designed for data from
incremental verification tasks, would be needed. We cannot offer such
a model here, but can only the offer a first step in that
direction. More importantly, though, the only part of
(\ref{bsp:observed-preferences}) that might plausibly change for a
more encompassing model along the lines sketched above is that the 3
\emph{false} answers in the \as-conditions with neutral intonation
might support the conclusion that the local reading is attested. But
this hypothetical effect will certainly be no bigger than marginal,
and so no genuinely different conclusions of theoretical relevance
should be expected.

@@

The clearest upshot of theoretical importance of this study is that
strength-based meaning selection does not seem to be a good
disambiguation criterion for grammaticalism. This point is also
relevant in general, because disambiguation based on logical strength
has been suggested in other domains as well
\citep[e.g.][]{DalrympleKanazawa1998:Reciprocal-Expr,CobrerosEgre2012:Tolerant-Classi}.
We tentatively suggested an alternative selection principle for
grammaticalism in terms of ``parsing economy,'' but it remains to be
seen whether this is empirically successful in other domains as well.

>>>>

To deal with these methodological problems, this paper presents
results from an experimental study which presented sentence materials
auditorily and explicitly manipulated contrastive stress on embedded
scalar items. We employed an \emph{incremental verification task} in
which parts of a to-be-evaluated picture were hidden and only revealed
piece-wise at the participants’ request until they felt able to give a
binary truth-value judgement \citep[see][]{Conroy2008}. We use both a
classical regression analysis and a Bayesian statistical model to
analyze the data from this novel task, and validate this method by
including control conditions testing ambiguous sentences with a
well-known preference on available readings. We argue that this method
provides categorical behavioral data that is both indicative of the
reading preferences among participants and largely independent of
potential pictorial confounds, such as the mentioned typicality
effects.

@@

The paper is structured as follows. Section~\ref{sec:get-know-your}
elaborates on the three kinds of relevant readings for our target
sentences. Section~\ref{sec:theories-predictions} works out testable
\emph{ex ante} predictions of \emph{traditionalism} and
\emph{grammaticalism}. Section~\ref{sec:previous-studies} reviews
related experimental studies to the extent necessary to motivate our
own approach. Section~\ref{sec:exp} describes our experimental design,
analyses and results. Finally, Section~\ref{sec:critical-reflection}
discusses our method and interpretation of the results in a broader
theoretical context.

@@

\paragraph{General Idea.} In order to test the availability and
preferences of different readings of \as- and \es-sentences in German,
we were looking for a way to unambiguously map responses from a
picture verification task to specific readings. We were particularly
interested in the question whether local readings would be observed at
all, and whether their presence or absence would be modulated by a
contrastive accent on the scalar item. Moreover, we were interested in
obtaining information about the relative preferences of the different
readings. In addition, we wanted to minimize potential picture
typicality effects. To achieve this (see
Section~\ref{sec:discussion-1} for discussion), we used an
\emph{incremental verification task} (\acro{ivt}), which is a
modified version of picture verification
\citep[see][]{Conroy2008}. The general idea is that subjects are
requested to judge sentence material with respect to pictures that do
not necessarily contain all the information relevant for judging a
certain reading true or false. In that case, participants can demand
that more information be revealed. Participants are instructed to make
a truth-value judgment as soon as they are able to. When they do, the
trial ends.

@@

The number of responses that fell out of our classification scheme
differs substantially between \as- and \es-conditions. There are 7.0\%
/ 4.4\% unclassifiable judgements in the neutral / accented
\as-conditions, but 19.3\% / 17.6\% in the neutral / accented
\es-conditions respectively. A look at the left-hand side of
Table~\ref{tab:count_data_CC} reveals that there is some systematicity
in 'error' answers. Most answers that we classified as 'errors' have a
plausible explanation: random errors, a handful of mistakes resulting
from confusing buttons for \emph{true} and \emph{false} and a few
'spill-over errors' where participants gave responses one position too
late. There is one notable exception, though. A substantial number of
\emph{true} responses were given at the second position of
\es-sequences (9.7\% / 8.8\%) which is shown in
Figure~\ref{fig:exseqES2}. Although this position in the sequence is
the critical position to reveal a global reading, the latter would be
indicated by a \emph{false} response. Given the low number of mistakes
attributable to confusion of buttons for \emph{true} and \emph{false}
elsewhere, this seems to be a more systematic pattern. It appears as
if subjects read \es-sentences as if the non-monotonic quantifier
\emph{exactly one} was a monotonic \emph{at least one}, without
pragmatic enrichment of \emph{some}. 16 out of the total 21 answers in
this category come from 5 subjects, while the remaining 5 were single
answers by 5 different subjects.
% subjects 1, 9, 12, 21, 84
This suggests that at least for some subjects non-monotonic
quantifiers were problematic. (We will come back to this intriguing
observation later in Section~\ref{sec:discussion-1}, where we suggest
that a non-monotonic reading of \emph{exactly one} might also explain
the high number of \emph{true} answers in step 5 of the
\es-conditions.)

@@

\paragraph{Summary \& Interpretation.} % The present study investigated
% prosodic effects on quantifier interpretation by employing a new
% experimental paradigm, the incremental verification task. We were
% specifically interested in whether ``local readings'' of sentences
% where \emph{some} is embedded under another quantifier can be found,
% and how salient these readings are under varying prosody of auditorily
% presented sentence material, in particular the presence or absence of
% contrastive stress on embedded \emph{some}.
%
High scores of success in control conditions show that participants
understood the incremental verification task and were able to give
judgements at the right point in a picture sequence. Results for the
preference-related controls show that our design is able to detect
multiple readings and preferences among these. Crucially, the amount
of response types for \lc- and \ec-readings reflected the known
preference for the former, with a mild bias for readings that can be
judged later in the sequence. Also, the incremental verification task
was generally sensitive to prosody. However, our regression analysis
showed that significant prosodic effects were restricted to
preference-related controls. Contrastively, the Bayesian analysis
showed that accenting scalar \emph{some} generally led to more local
readings, but that effect was not significant. Local readings occurred
in \es-sentences, independently of prosody, but required prosodic
marking in \as-sentences. Our analyses support the impression that
inspection of the raw data gives, namely that the general qualitative
pattern of reading preferences is the same for \as- and
\es-conditions: literal readings are preferred over local readings
which are preferred over global readings. More concretely, our
analyses suggest the following preference patterns (bracketed readings
are not supported by our data and the previous analyses):

@@

Traditionalism easily explains the absence of global readings. Weak
traditionalism, introduced in Section~\ref{sec:traditionalism}, for
instance, would hold that the extra assumptions needed to derive
global readings (e.g., a speaker competence assumption) are not
available or only allow for epistemically weak implicatures that would
show as responses indicative of literal readings in our task. In
support of this view, traditionalists could argue that the task's
rather high processing demands lead to a suppression of global
readings, in line with the findings of
\citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
load negatively affects the number of scalar implicature responses in
sentence verification tasks. The finding of local readings in
\as-sentences with contrastive stress is easily explained by adopting
the prosodic markedness hypothesis. What traditionalism does not
predict is the high number of answers indicative of local readings in
the \es-conditions. Resorting to the prosodic markedness hypothesis
does not help, because local readings were observed for accented as
well as for unaccented \es-sentences.%  It would also remain unclear why
% prosodic cues should have such differential effects on \as- and
% \es-sentences.

@@

On conceptual grounds we are very much in favor of a disambiguation
criterion in terms of economy considerations, but whether the
particular account sketched here is empirically successful in other
cases as well, must remain to be seen. Two things are worth
emphasizing here nonetheless. Firstly, the sketched Magri-style
account is a plausible alternative \emph{post hoc} explanation. It was
not, at least to our knowledge, a salient possibility before seeing
our data set: other specifications of $Alt_1$ and $Alt_2$ could have
been made equally plausible \emph{ex ante}. Secondly, what our data
refutes is that preferences for readings follow logical
strength. This, therefore, does not jeopardize grammaticalism as a
core theory, but calls for theory-internal revision of its
disambiguation criterion. Taken together, we argue that the data
presented here points to a dire need of refining grammaticalism,
perhaps along the lines suggested here, but ideally alongside more
experimental data.

\paragraph{Traditionalism.} Traditionalism, as we described it in
Section~\ref{sec:theories-predictions}, can also not account for the
observed pattern of results. It has to explain the possibility of
local readings of prosodically unmarked \es-sentences, and, perhaps,
also the large number of local readings in accented \es-sentences
compared to the much lower number in accented \as-sentences. A first
option might be to account for alleged local readings as the result of
some other phenomenon, such as typicality or contrast
\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Embedded-Scalar,Tielvan-Tiel2014:Quantity-Matter}.
Since this ties into a critical reflection on our design, we will
enlarge on the possibility of typicality- and contrast-based effects
in our setting. Eventually, we argue that contrast-effects alone are
unlikely to explain the observed high number of local answers in
\es-sentences, but that a ``modern traditionalist'' explanation of the
answer pattern might be available if we allow for the possibility that
\emph{exactly one} gets an unexpected ``referential interpretation.''

@@

The foregoing discussion presupposed that the interpretation of our
data, given in Section~\ref{sec:discussion-1}, was sound. But there
are a number of conceivable objections that cast into doubt that our
data suggests the preference relation in
(\ref{bsp:observed-preferences}). We will consider the most pressing
ones in the following.

@@

\paragraph{Incomparability of target conditions and preference-related
  controls.} One could object that it is not feasible to compare
results from the preference-related controls to results from our
target conditions, because the source of different readings is
fundamentally different. In the former we have a syntactic ambiguity,
in the latter a set of putative pragmatic enrichments. The former is a
case of perceived ambiguity (some of our subjects reported this), the
latter arguably is not
\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
if the distribution of responses is indicative of the true preference
patterns in preference-related controls, this would not necessarily
mean that the distribution of responses in target conditions is
indicative of preference relations in the same way.

@@

To address this worry we ran another stripped-down version of the
\ivt. We recruited 50 subjects via Amazon's Mechanical Turk and paid
them 1 US\$ compensation. Similar to our main experiment, the
post-experiment started with two training trials with unambiguous
sentences, familiarizing our subjects with the task. In the
browser-based version, alert boxes pointed out subjects' mistakes when
they tried to exit too early, chose the wrong response or tried to
unravel the sequence further than strictly necessary. The main part of
the experiment consisted of six trials, two of which were critical and
four of which were controls. On critical trials, each subject saw
different version of sentences like (\ref{bsp:Item-PostExp}), in
connection with sequences like in Figure~\ref{fig:Trial-PostExp}.

@@

If we accept that the \ivt is sensitive to implicature-based
ambiguities, what is left to worry about is that information about
response biases (early vs.~late) do not carry over from the
preference-related control conditions to the target conditions in the
main experiment. It could be, after all, that the task triggers
subjects to exit late for perceived syntactic ambiguities and to exit
early for ``pragmatic ambiguities'' involving implicature
readings. But none of this has any serious impact on the suggested
preference relation in (\ref{bsp:observed-preferences}). For even if
there is a sequential bias in the target conditions to exit early, the
main effect of such a bias would merely be that we should consider
local readings more salient than we do now. In the light of the data
from main and post-experiments, it would be far-fetched to uphold that
our data indicates that local readings are at least as salient as
literal ones. But that means that the suggested interpretation in
(\ref{bsp:observed-preferences}) still holds, and all the problems
that we identified for (the considered versions of) traditionalism and
grammaticalism apply.

% To strengthen this case further, let us assume that the \ivt is
% entirely incapable of reliably indicating preferences among candidate
% pragmatic enrichments of the relevant kind. Can we still draw any
% conclusions about mere availability (non-negligible salience) of
% readings? At a minimum, we would like to uphold that local readings
% are available in \es-sentences and that global readings are unattested
% in \as- and \es-sentences. But that alone is not predicted by either
% traditionalism or grammaticalism in the guises that we considered. The
% former cannot explain the substantial number of local responses in
% \es-sentences, the latter does not explain the total absence of global
% responses.

@@

Still, we readily admit that our model is highly simplistic. Several
aspects are especially noteworthy here. Firstly, we did not
distinguish different types of errors, and did not take into account
that when errors occurred earlier in the sequence, later decision
points could no longer be reached. This way the model may actually
have unduly de-emphasized the salience of readings that can be judged
later in a sequence. Another, more complicated model of the likelihood
of answer patterns, might therefore have given support to
quantitatively different conclusions. Unfortunately, it is not clear
how exactly such a more complex generating model should be
set-up. Eventually, a full processing model, designed for data from
incremental verification tasks, would be needed. We cannot offer such
a model here, but can only the offer a first step in that
direction. More importantly, though, the only part of
(\ref{bsp:observed-preferences}) that might plausibly change for a
more encompassing model along the lines sketched above is that the 3
\emph{false} answers in the \as-conditions with neutral prosody
might support the conclusion that the local reading is attested. But
this hypothetical effect will certainly be no bigger than marginal,
and so no genuinely different conclusions of theoretical relevance
should be expected.

@@

The clearest upshot of theoretical importance of this study is that
strength-based meaning selection does not seem to be a good
disambiguation criterion for grammaticalism. This point is also
relevant in general, because disambiguation based on logical strength
has been suggested in other domains as well
\citep[e.g.][]{DalrympleKanazawa1998:Reciprocal-Expr,Winter2001:Plural-Predicat,CobrerosEgre2012:Tolerant-Classi}.
We tentatively suggested an alternative selection principle for
grammaticalism in terms of ``parsing economy,'' but it remains to be
seen whether this is empirically successful in other domains as well.
